Sketch of DP - Bayesian Inference

### 2018-07-15 main-sketch.tex
rewrite section2

\section{Problem Statement}
Our research is based on an observation that under different measurement, mechanisms usually have different accuracy behavior. When adding noise according to a certain measurement, mechanism' accuracy behavior will be better than when adding noise according to other measurements. Here we study the private Bayesian inference based on Hellinger distance measurement. Showing that our newly-designed mechanism adding noise according to Hellinger distance performs better than baseline mechanism adding noise according to $l_1$ norm.

>>>>

\section{Problem Statement}
The posterior belief from Bayesian inference is usually represented by a probabilistic distribution like $\betad(\alpha, \beta)$. When we try to make this distribution public, sensitive information of the data based on which the posterior drew from can be compromised. So, it is important to protect this posterior distribution. When our protection objective is a distribution rather than a numeric value or vector, it would be better to measure the accuracy by distance over distributions, for instance, Hellinger distance, than by numeric metrics like $\ell_1$-norm. Our research is based on the observation that under metrics over distribution, mechanisms usually have different behavior from under metrics over numeric values. If we measure accuracy based on distribution metrics, then mechanisms adding noise according to distribution measurements can out-performs mechanisms' adding noise according to numeric measurements.
